%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Classicthesis-Styled CV
% LaTeX Template
% Version 1.0 (22/2/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{scrartcl} % From the koma-script package

\reversemarginpar{} % Move the margin to the left of the page

\usepackage[nochapters]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage[LabelsAligned]{currvita} % Use the currvita style for the layout of the document

\renewcommand{\cvheadingfont}{\LARGE} % Font color of your name at the top
% TODO Commenting out colors for now, check again later
% \renewcommand{\cvheadingfont}{\LARGE\color{MidnightBlue}} % Font color of your name at the top

\usepackage{hyperref} % Required for adding links	and customizing them
% TODO Commenting out colors for now, check again later
% \hypersetup{colorlinks, breaklinks, urlcolor=MidnightBlue, linkcolor=MidnightBlue} % Set link colors

\newlength{\datebox}\settowidth{\datebox}{Spring 2011} % Set the width of the date box in each block

\newcommand{\Description}[2]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{\MarginText{#1}#2}\par\normalsize\vspace{0.5em}} % Define a command for descriptions of each entry - change spacing and font sizes here

% Define a command for each new block - change spacing and font sizes here: #1 is the main title, #2 and #3 form the description
\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0 #1
\vspace{0.25em}

\Description{#2}{#3}

}

% Command for creating person info items, #1 is name of field, #2 is value
% ex usage \PersonalInfoItem{email}{nickgirardo@gmail.com}
\newcommand{\PersonalInfoItem}[2]{\noindent \small \MarginText{\textit{#1}}\hspace{2em}#2
\vspace{0.25em}} % Add some white space after each new entry

\usepackage[marginparsep=-1em, bottom=1em, top=8em]{geometry}
\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1\/}} % New command defining the margin text style

\newcommand{\SectionName}[1]{\noindent\spacedlowsmallcaps{#1}\vspace{0.25em}}

%----------------------------------------------------------------------------------------

\begin{document}

\thispagestyle{empty} % Stop the page count at the bottom of the first page

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\begin{cv}{\spacedallcaps{Nick Girardo}}\vspace{1.5em} % Your name

% Personal information heading
\SectionName{Personal Information}

% Email address
\PersonalInfoItem{email}{\href{mailto:nickgirardo@gmail.com}{nickgirardo@gmail.com}}

% Personal website
\PersonalInfoItem{website}{\href{https://www.nickgirardo.com/}{https://www.nickgirardo.com/}}

% Github profile
\PersonalInfoItem{github}{\href{https://github.com/nickgirardo}{nickgirardo}}

% Phone number
\PersonalInfoItem{phone}{+1 (856) 520-5481} % chktex 8

\vspace{1em} % Extra white space after the personal information section

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\SectionName{Work Experience}

\NewEntry{Software Engineer -- OnSiteIQ Inc.}{February 2019--\newline April 2021}{Developed and maintained SaaS web application.\newline Managed new features and changes through testing, production, and deployment.} % chktex 8

%------------------------------------------------

\NewEntry{Software Engineer -- Sketchdeck Inc.}{October 2016--\newline February 2018}{Developed and maintained SaaS web application.\newline Designed, proposed, developed, and deployed internal and external tools.} % chktex 8

%------------------------------------------------

\NewEntry{Software Engineering Intern -- Addteq Inc.}{Summer 2015}{Designed and developed platform for automatic setup of Atlassian tools.} % chktex 8

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------

\SectionName{Projects}

\NewEntry{WebAssembly Boids}{Fall 2018}{Classic boids simulation running in hand-written WebAssembly.\newline Exploration of WebAssembly's interface and performance.\newline View demo: \href{https://nickgirardo.github.io/animation-tests/wasm-boids/}{hsttp://nickgirardo.github.io/animation-tests/wasm-boids/}\newline View source: \href{https://github.com/nickgirardo/wasm-boids}{https://github.com/nickgirardo/wasm-boids}}

\NewEntry{Cel Shaded AA Demo -- WebGL 2 Port}{Fall 2018}{WebGL 2 port of Philip Rideout's ``Antialiased Cel Shading'' demo.\newline Exploration of shading and tesselation in WebGL 2.\newline View demo: \href{https://nickgirardo.github.io/trefoil/}{https://nickgirardo.github.io/trefoil/}\newline View source: \href{https://github.com/nickgirardo/wasm-boids}{https://github.com/nickgirardo/wasm-boids}} % chktex 8

\NewEntry{Context Play/ Pause}{Summer 2018}{Firefox WebExtension allowing users to play or pause videos from a tab's context menu.\newline View Add-on: \href{https://addons.mozilla.org/en-US/firefox/addon/context-play-pause/}{https://addons.mozilla.org/en-US/firefox/addon/context-play-pause/}\newline View source: \href{https://github.com/nickgirardo/context-play-pause}{https://github.com/nickgirardo/context-play-pause}}

\NewEntry{Grid Tetris}{Summer 2018}{Experimental implementation of classic video game Tetris using CSS Grid for all display.\newline View demo: \href{https://nickgirardo.github.io/grid-tetris/}{https://nickgirardo.github.io/grid-tetris/}\newline View source: \href{https://github.com/nickgirardo/grid-tetris}{https://github.com/nickgirardo/grid-tetris}}

\NewEntry{Phone.WTF}{Fall 2015}{Prank your unsuspecting friends and family by connecting them through a phone call.\newline Uses the Twilio API and a Python/ Flask backend.\newline Created at Fall 2015 HackNY Hackathon, winner of PayPal prize.\newline View source: \href{https://github.com/nickgirardo/PhoneWtf}{https://github.com/nickgirardo/PhoneWtf}}

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\SectionName{Education}

\NewEntry{Rutgers, the State University of New Jersey, New Brunswick}{2012-2016}{Major in Computer Science, School of Arts and Sciences} % chktex 8

\vspace{1em} % Extra space between major sections


\end{cv}

\end{document}
